### 2017-03-06 Writing/draft.tex
Added proof for CD metric equation 5

\section{Acknowledgements}
European Research Council under the European Union’s Seventh Framework Programme (FP/2007–2013)/ERC Grant Agreement number 311092.
Cluster acknowledgements
Bertie

@@

As described in equations \ref{Positivity}, \ref{Identity} and \ref{Equality},

\begin{equation}
    \label{subadditivity_demo}
    \begin{aligned}
    &0\leq CD_{x,z} \leq 1\\
    &\text{and}\\
    &0\leq CD_{z,y} \leq 1\\
    &\text{thus}\\
    &0\leq CD_{x,z} + CD_{z,y}  \leq 2\\
    \end{aligned}
\end{equation}

\subsubsection{Case 1}
If $CD_{x,z} = 0$, then, following \ref{Identity}:

\begin{equation}
    \label{subadditivity_demo_case1}
    \begin{aligned}
    &CD_{x,z} = CD_{z,y} = CD_{x,y}\\
    &\text{then}\\
    &CD_{x,y} \leq CD_{x,z} + CD_{z,y}\\
    \end{aligned}
\end{equation}

\subsubsection{Case 2}
If $CD_{x,z} > 0$, then:

\begin{equation}
    \label{subadditivity_demo_case2}
    \begin{aligned}
    &CD_{x,z} = CD_{z,y} = CD_{x,y}\\
    &\text{then}\\
    &CD_{x,y} \leq CD_{x,z} + CD_{z,y}\\
    \end{aligned}
\end{equation}

% \subsubsection{Character difference metric is ontological (identity of indiscernibles)}

% \begin{equation}
%     \label{CDnull}
%     CD_{(x,y)} = 0 \Leftrightarrow x = y
% \end{equation}
% This is because of equation \ref{equality}; in fact $x$ and $y$ is actually expressed in terms of phylogenetic information per character (i.e. normalised for character state token).

% \subsubsection{Character difference metric is sub-additive (triangle inequality)}

% \begin{equation}
%     \label{subadditive}
%     CD_{(x,y)} \leq CD_{(x,z)} + CD_{(z,y)}
% \end{equation}
% Following equations \ref{CDpositive}, \ref{equality}, \ref{CDnull}.

% Thus:

% \begin{equation}
%     d: \frac{\abs*{\sum_{i}^{n}(x_{i} - y_{i})}{n} \rightarrow [0;1]
% \end{equation}

% Thus:

% \begin{equation}
%     d: \frac{\sum_{i}^{n}(x_{i} - y_{i})}{n} \rightarrow [0;1]
% \end{equation}

>>>>

\section{Acknowledgements}
European Research Council under the European Union’s Seventh Framework Programme (FP/2007–2013)/ERC Grant Agreement number 311092.
Cluster acknowledgements
Bertie
Guillermo Herraiz Yebes for helping with the CD metric proof.

@@

\begin{equation}
    \label{subadditivity_demo}
    \begin{aligned}
    CD_{x,y} &\leq CD_{x,z} + CD_{z,y}\\
    1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right)
     &\leq 
     1 - \left(\frac{\abs*{\frac{\sum_{k}^{j}\abs{x_{k}-y_{k}}}{j}-\frac{1}{2}}}{\frac{1}{2}}\right) 
     +
     1 - \left(\frac{\abs*{\frac{\sum_{a}^{b}\abs{x_{a}-y_{a}}}{b}-\frac{1}{2}}}{\frac{1}{2}}\right) \\
    \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} 
     &\geq 
     \abs*{\frac{\sum_{k}^{j}\abs{x_{k}-y_{k}}}{j}-\frac{1}{2}}
     +
     \abs*{\frac{\sum_{a}^{b}\abs{x_{a}-y_{a}}}{b}-\frac{1}{2}} - 2\\
          % Add brackets symbols
     \in[0,\frac{1}{2}] &\geq (-2) \in[0,\frac{1}{2}] \in[0,\frac{1}{2}]\\
     \in[0,\frac{1}{2}] &\geq \in[-2,-1]\\
    \end{aligned}
\end{equation}
